
\documentclass[a1paper]{article}

\usepackage[left=12.41cm,right=12.41cm,bottom=10cm,landscape]{geometry}
\usepackage{multicol}
\usepackage{verbatim}
\usepackage{float}
\usepackage{graphicx}
\usepackage{textcomp}

\setlength{\parindent}{0cm}
\setlength{\parskip}{0.8em}

% Remove the author and date fields and the space associated with them
% from the definition of maketitle!
\makeatletter
\renewcommand{\@maketitle}{
\newpage
 \null
 \begin{center}
  {\LARGE \@title \par}
 \end{center}
 \vskip 2em
 \par} \makeatother


\title{The Paste Down}
%subtitle{Untitled Volume I}
       
      

\begin{document}

\maketitle

\thispagestyle{empty}
\pagestyle{empty}

\begin{multicols}{7}{







\section{Untitled}
Am 11.09.2012 12:29, schrieb Eul:
> Hallo Piraten, allen gewählten Piraten von den Evinger Piraten ,, herzlichen Glückwunsch,, zur Wahl.

Herzlichen Dank von den Piraten in Brackel-Nord für deine Worte. Diese und nicht zuletzt deren Form lassen mich mit unserem Beschluss, euch energisch unter die Arme zu greifen, jetzt endlich an das Parteivolk herantreten. Wir verstehen völlig eure Probleme, den Grundsätzen der Partei, also Dinge wie Protokolle von Sprecherwahlen und sonstigen Beschlüssen wie etwa einer Wahlvorgabe an die Piraten zur Unterstützung der Bürgerliste, gerecht zu werden. Wir sind uns nicht im Klaren darüber, ob der Ortsverein Eving bereits gegründet wurde, aber wir sichern euch unsere volle Unterstützung bei der Gründung zu. Es kann nicht sein (!), dass die wertvolle Zeit am Sonntag, in der man wunderbar programmatisch arbeiten oder Pressemitteilungen hätte formulieren können, durch die zum Scheitern verurteilten basisdemokratischen Bestrebungen von normalem Parteiplebs gestohlen wird! Ein Vorstand muss endlich die Schirmherrschaft über Versammlungen übernehmen, es kann nicht angehen, dass Versammlungsleiter da dem vorgeblichen Willen von irgendwelchen jungen Hunden nachgeben. Straff durch Leitanträge die Sache in 90 Minuten durchgezogen, danach zum Kreisligaspiel und mit den anwesenden Dorfgranden die Aufstellung der Verkaufsbuden am Wochenmarkt ausbaldowern, so hat der piratige Sonntag auszusehen. Wir sind uns mit dem Ortsquadrat Persebeck einig, dass eine Partei sich solche Spielchen wie diesen dezentralen Kram einfach nicht leisten kann, und wenn es doch sein muss, dann sollen das gefälligst andere machen, wir sind Dortmund, was kümmert uns der Rest der Partei!

Wir verstehen euren Frust und können in in Gänze nachvollziehen. Über Wochen vorbereitet verpuffte der Knall des Wechsels eines Mandatsträgers ungehört, weil der Mandatsträger einfach nicht wieder gewählt wurde. Solche PR-Fails kann und darf sich die Partei nicht länger leisten, denkt doch mal an die Außenwirkung! Jetzt muss der arme Vertreter der Bürgerliste so ganz geräuschlos beitreten. Ärgerlich, das hätte man professioneller handhaben müssen! An dieser Stelle jedoch möchten wir den wenigen eingeweihten Piraten ind Dortmund jedoch unseren Respekt aussprechen. Es stimmt uns hoffnungsvoll, dass solche lang geplanten Dinge erfolgreich vor dem Rest des Stimmviehs verborgen werden konnten. Ein Platz in der Bezirksvertretung erfordert gewisse Opfer, die wir mit euch absolut bereit sind zu bringen.

Wir in Brackel-Nord sind uns mit Eving einig, dass nur die Bildung von schlagkräftigen Kleinzellen mit entsprechender feststehender Finanzierung der einzige Weg sind, um die Gesichter bekannter Lokalpolitiker unter dem Logo der Piraten an die Masten zu bekommen. Es ist nicht mehr viel Zeit bis zur nächsten Wahl und wir MÜSSEN dann zur Wochenmarktsituation in Lastrop eine Meinung haben! Auch in unseren Reihen gibt es Leute, die Bekannte von Schaustellern kennen, nur mit einem entsprechenden Rückhalt bei dieser unserer Wählerklientel haben wir eine Chance!


> Leider konnten wir nicht mitabstimmen da wir nach zweieinhalb Stunden Wartezeit ( technische Probleme ) die Heimreise angetreten haben. (...) Hinzu kommt noch, daß wir an den Abstimmungen nicht teil nehmen konnten. Man hat uns  die Möglichkeit genommen, mit unseren Stimmen Einfluss auf die Wahl zu nehmen.


Die Piratenpartei Brackel-Nord zeigt sich zutiefst solidarisch und ist betrübt über diesen Verstoß gegen das Parteiengesetz. Wir überlegen derzeit, ob wir einen Notfallfonds für den Gang zu den Gerichten auflegen sollen, da die Klage gegen diesen Verstoß gegen die Mitgliederrechte durch diese laschen Parteischiedsgerichte wohl nicht in unserem und eurem Sinne entschieden wird. Die spontane Äußerung eines Brackel-Nord Piraten "zur Not dann bis vor den europäischen Gerichtshof für Menschenrechte!" haben wir aus Außenwirksamkeitsgründen dann aus dem Protokoll gestrichen.

Am Ende des Tages bleibt uns jetzt nur, euch solidarliberalische Grüße zu übersenden.

weggetreten!

Holger

-- 

Mailingliste der Piratenpartei in Dortmund




\begin{figure}
%\centering
\vskip 4em%
\begin{verbatim}
<div id="outer">
<div id="container">
I am 960px wide
</div>
</div>
\end{verbatim}
\vskip 1em
\caption{-- Untitled}
\vskip 3em%
\label{960px}
\end{figure}


\section{A Guide in UNIX Hacking.}
\begin{verbatim}
**************************************
*       A beginners guide to:        *
*          H A C K I N G             *
*                                    *
*                U N I X             *
*                                    *
*          By Jester Sluggo          *
*         Written 10/08/85           *
**************************************
\end{verbatim}

  In the following file, all references made to the name Unix, may also be
substituted to the Xenix operating system.

  Brief history:  Back in the early sixties, during the development of third
generation computers at MIT, a group of programmers studying the potential of
computers, discovered their ability of performing two or more tasks
simultaneously.  Bell Labs, taking notice of this discovery, provided funds for
their developmental scientists to investigate into this new frontier.  After
about 2 years of developmental research, they produced an operating system they
called "Unix".

  Sixties to Current:  During this time Bell Systems installed the Unix system
to provide their computer operators with the ability to multitask so that they
could become more productive, and efficient.  One of the systems they put on the
Unix system was called "Elmos".  Through Elmos many tasks (i.e.  billing,and
installation records) could be done by many people using the same mainframe.

  Note:  Cosmos is accessed through the Elmos system.

  Current:  Today, with the development of micro computers, such multitasking
can be achieved by a scaled down version of Unix (but just as powerful).
Microsoft,seeing this development, opted to develop their own Unix like system
for the IBM line of PC/XT's.  Their result they called Xenix (pronounced
zee-nicks).  Both Unix and Xenix can be easily installed on IBM PC's and offer
the same functions (just 2 different vendors).

  Note:  Due to the many different versions of Unix (Berkley Unix, Bell System
III, and System V the most popular) many commands following may/may not work.  I
have written them in System V routines.  Unix/Xenix operating systems will be
considered identical systems below.

  How to tell if/if not you are on a Unix system:  Unix systems are quite common
systems across the country.  Their security appears as such:

\begin{verbatim}
Login;     (or login;)
password:
\end{verbatim}

  When hacking on a Unix system it is best to use lowercase because the Unix
system commands are all done in lower- case.

  Login; is a 1-8 character field.  It is usually the name (i.e.  joe or fred)
of the user, or initials (i.e.  j.jones or f.wilson).  Hints for login names can
be found trashing the location of the dial-up (use your CN/A to find where the
computer is).

  Password:  is a 1-8 character password assigned by the sysop or chosen by the
user.

\begin{verbatim}
      Common default logins
   --------------------------

   login;       Password:

   root         root,system,etc..
   sys          sys,system
   daemon       daemon
   uucp         uucp
   tty          tty
   test         test
   unix         unix
   bin          bin
   adm          adm
   who          who
   learn        learn
   uuhost       uuhost
   nuucp        nuucp
\end{verbatim}

  If you guess a login name and you are not asked for a password, and have
accessed to the system, then you have what is known as a non-gifted account.  If
you guess a correct login and pass- word, then you have a user account.  And,
if you guess the root password, then you have a "super-user" account.  All Unix
systems have the following installed to their system:  root, sys, bin, daemon,
uucp, adm

  Once you are in the system, you will get a prompt.  Common prompts are:

\begin{verbatim}
$
%
#
\end{verbatim}


  But can be just about anything the sysop or user wants it to be.

  Things to do when you are in:  Some of the commands that you may want to try
follow below:

  who is on (shows who is currently logged on the system.)
  write name (name is the person you wish to chat with)
  To exit chat mode try ctrl-D.
  EOT=End of Transfer.
  ls -a (list all files in current directory.)
  du -a (checks amount of memory your files use;disk usage)
  cd\\name (name is the name of the sub-directory you choose)
  cd\ (brings your home directory to current use)
  cat name (name is a filename either a program or documentation your username
has written)

  Most Unix programs are written in the C language or Pascal since Unix is a
programmers' environment.

  One of the first things done on the system is print up or capture (in a
buffer) the file containing all user names and accounts.  This can be done by
doing the following command:


\begin{verbatim}
cat /etc/passwd
\end{verbatim}



  If you are successful you will a list of all accounts on the system.  It
should look like this:

\begin{verbatim}
root:hvnsdcf:0:0:root dir:/:
joe:majdnfd:1:1:Joe Cool:/bin:/bin/joe
hal::1:2:Hal Smith:/bin:/bin/hal
\end{verbatim}


  The "root" line tells the following info :

\begin{verbatim}
login name=root
hvnsdcf   = encrypted password
0         = user group number
0         = user number
root dir  = name of user
/         = root directory
\end{verbatim}

  In the Joe login, the last part "/bin/joe " tells us which directory is his
home directory (joe) is.

  In the "hal" example the login name is followed by 2 colons, that means that
there is no password needed to get in using his name.

  Conclusion:  I hope that this file will help other novice Unix hackers obtain
access to the Unix/Xenix systems that they may find.  There is still wide growth
in the future of Unix, so I hope users will not abuse any systems (Unix or any
others) that they may happen across on their journey across the electronic
highways of America.  There is much more to be learned about the Unix system
that I have not covered.  They may be found by buying a book on the Unix System
(how I learned) or in the future I may write a part II to this........




\begin{figure}
%\centering
\vskip 4em%
\begin{verbatim}
<canvas id='world'></canvas>
\end{verbatim}
\vskip 1em%
\caption{-- Untitled}
\vskip 3em%
\label{960px}
\end{figure}





\section{T-h3x D0xed}

Handle: T-h3x

Justin Bieber Address \#1:

\setlength{\parskip}{0cm}
Justin Bieber 

c/o Island Def Jam Group

Worldwide Plaza 825 8th Ave 28th Floor

New York, NY 10019 USA 

\vskip 1em%
Justin Bieber Address \#2:

Justin Bieber 

P.O. Box 578, Wittmann, AZ 

Household Carina Bieber


\vskip 1em%
Justin Bieber Address \#3:

Justin Bieber 

4184573 Kinettie Rd. 

Atlanta Georgia

\vskip 1em%
-====================-

@ANONCELEBS

-====================-
\setlength{\parskip}{0.8em}






\begin{figure}
%\centering
\vskip 4em%
\begin{verbatim}
Hippo test
\end{verbatim}
\vskip 1em%
\caption{-- Untitled}
\vskip 3em%
\label{960px}
\end{figure}



\section{House}
\begin{verbatim}
print("Building house")
print("Ingredients must be in slots 1-5")

local function wall()
for i=1, 9 do
if windows==1 and (i==5 or i==6) then
turtle.select(5)
turtle.placeDown()
turtle.select(2)
elseif windows==2 and (i==5 or i==6) then
turtle.select(5)
turtle.placeDown()
turtle.select(3)
else
turtle.placeDown()
end
turtle.forward()
end
turtle.turnLeft()
end

--Each layer is 4x10
local function layer()
for k=1, 4 do
wall()
end
turtle.up()
end

--INITIATION + BASE LAYERS
turtle.up()
turtle.turnRight()
turtle.select(1)
layer()
wall()
wall()
turtle.select(2)
wall()
wall()
windows=1
turtle.up()
layer()
windows=2

--ROOF LAYERS
turtle.select(3)
layer()
turtle.forward()
turtle.turnLeft()
turtle.forward()
turtle.turnRight()
for z=1, 4 do
for i=1, 7 do
if turtle.getItemCount(3) == 0 then
turtle.select(4)
end
turtle.placeDown()
turtle.forward()
end
turtle.turnLeft()
end
turtle.up()
turtle.forward()
turtle.turnLeft()
turtle.forward()
turtle.turnRight()
for z=1, 4 do
for i=1, 5 do
turtle.placeDown()
turtle.forward()
end
turtle.turnLeft()
end
turtle.up()
turtle.forward()
turtle.turnLeft()
turtle.forward()
turtle.turnRight()
for z=1, 4 do
for i=1, 3 do
turtle.placeDown()
turtle.forward()
end
turtle.turnLeft()
end
turtle.up()
turtle.forward()
turtle.turnLeft()
turtle.forward()
turtle.turnRight()
for z=1, 4 do
for i=1, 1 do
turtle.placeDown()
turtle.forward()
end
turtle.turnLeft()
end
turtle.forward()
turtle.turnRight()
for z=1, 5 do
turtle.forward()
turtle.down()
end
turtle.down()
turtle.down()
turtle.down()
turtle.turnRight()
for z=1, 4 do
turtle.forward()
end
print("Mission copmleted.")
\end{verbatim}



\section{Subadhra pacifies Draupadi}
Subadhra pacifies Draupadi

===============================

\setlength{\parskip}{0cm} 
(Extract from 'The Mahabharata' of Krishna-Dwaipayana Vyasa BOOK 1 "Adi-parva"
\setlength{\parskip}{0.8em}
 
Translated into English Prose from the Original Sanskrit Text
 
by Kisari Mohan Ganguli [1883-1896]
\setlength{\parskip}{0.0em}

===============================

\setlength{\parskip}{0.8em}

...'Arjuna returned to Dwaraka and was united in marriage
with Subhadra. Worshipped by the sons of Vrishni's race, Arjuna, sporting
there as he pleased, passed a whole year in Dwaraka. The last year of his
exile the exalted one passed at the sacred region of Pushkara. After the
twelve years were complete he came back to Khandavaprastha. He approached
the king first and then worshipped the Brahmanas with respectful
attention. At last the hero went unto Draupadi. Draupadi, from jealousy,
spoke unto him, saying, 'Why tarriest thou here, O son of Kunti? Go where
the daughter of the Satwata race is! A second tie always relaxeth the
first one upon a faggot!' And Krishna lamented much in this strain. But
Dhananjaya pacified her repeatedly and asked for her forgiveness. And
returning soon unto where Subhadra, attired in red silk, was staying,
Arjuna, sent her into the inner apartments dressed not as a queen but in
the simple garb of a cowherd woman. But arrived at the palace, the
renowned Subhadra looked handsomer in that dress. The celebrated Bhadra
of large and slightly red eyes first worshipped Pritha. Kunti from excess
of affection smelt the head of that girl of perfectly faultless features,
and pronounced infinite blessing upon her. Then that girl of face like
the full moon hastily went unto Draupadi and worshipped her, saying, 'I
am thy maid!' Krishna rose hastily and embraced the sister of Madhava
from affection, and said, 'Let thy husband be without a foe!' Bhadra
then, with a delighted heart, said unto Draupadi, 'So be it!' From that
time, O Janamejaya, those great warriors, the Pandavas, began to live
happily, and Kunti also became very happy.'
===============================





\section{ciudades DANE}

/*
tengo dos tablas, una que alguien hizo con las ciudades de Colombia con sus respectivos códigos que no se a que se refieren y la que yo cree con las ciudades sus respectivos departamentos y su códigos DANE representantes de dichas ciudades, ahora lo que quiero es por medio del nombre de la ciudad sacar aquellas ciudades que existen en la tabla que no hice yo, pero que no están en la tabla que yo hice, esto para que, pues voy a sacar datos de clientes, pero teniendo en cuenta la ciudad a la que están enlazados en la antigua tabla, este nombre compararlo en la nueva tabla y que me devuelva el código DANE de la ciudad el cual esta en mi nueva tabla, espero que entiendan lo que trato de explicar aca, el problema que tengo con el SQL es que no me hace la comparacion o la hago mal yo, no se la verdad, aca les dejo el SQL que estoy usando a ver que me pueden recomendar, muchas gracias por tomarce su tiempo y leer esto aca va el SQL 
*/
\begin{verbatim}
SELECT ci_ciudad.ci_id, ci_ciudad.ps_id, 
ci_ciudad.ci_nombre FROM ci_ciudad, 
ciudades_dane WHERE ciudades_dane.ciudad
!= ci_ciudad.ci_nombre
\end{verbatim}

\vskip 1em
/*
este debería sacarme las ciudades que estan en la tabla vieja, pero que no estan en la tabla nueva creo jeje!
*/











\section{Untitled}
Anonymous Message: GoDaddy

Hello Citizens of the world, We are Anonymous. Dear brothers and sisters. Now is the time to open your eyes and expose the truth! 

It has come to our attention that Go Daddy, an Internet domain registrar and web hosting company has gained the attention of anonymous and the world yesterday as it was experiencing "intermittent outages." 

As silly as it seems, many members of anonymous are still puzzled whether it was truly an Anonymous member or a government entity is still unknown. However, many of us have concluded that Go Daddy was taken down because of its support for SOPA, the "Stop Online Piracy Act."

Go Daddy has committed many blatant attempt to destroy the Civil rights of the Ninety Nine percent. Political website that contained stinging criticism of the Obama administration have been removed by Go Daddy because it was, in there words, "maliciously harmful to individuals in the government."

Therefor Anonymous asks the ninety nine percent to boycott Go Daddy and remove there hosting to another domain name servers.

Anonymous would like to point out that Go Daddy who is, currently running millions of sites around the world, is actively putting SOPA, a bill that was petitioned by four point five million people, into effect.

Manchurian Candidate, Barack Hussein Obama, has already committed many acts of destruction against the constitution of the United States claiming it as an "Imperfect document" and he has already signed such unconstitutional bills as NDAA "national defense Authorization Act"and Executive order NDRA "National Defense Resources Preparedness." These bills are violations to our constitutional and civil liberties.

People of the world, Our internet freedom is dwindling because of government tyranny. For the love of all our future and humanity, wake up and open your eyes before the United States of America follows in the footsteps of Communist China. 

We are Anonymous.
\setlength{\parskip}{0cm}

We are legion. 

We do not forgive.

we do not forget. 

Expect us. 
\setlength{\parskip}{0.8em}






\section{Untitled}

Untitled








\section{Arcade Gatcha Trade}
::BB:: Dwarf Hamster Gacha

I am looking for Panda 

I have to trade or sell at cost: Coffee, Fairy Lemon, Fairy Mint (2), Fairy Peach, Fairy Pistachio, Fairy Plum (2), Parti Dough (2), Siberian Cocoa, Siberian Snow (2), Siberian Soot (2), Sunshine

\vskip 1em

\setlength{\parskip}{0cm}

[Commoner] Monogram Marquee Light

Looking for N, I, A

Have for trade or sell at cost: B (2), C, D, G, J, K, L, Q, R, T, U (2), V, Z

\vskip 1em
The Sea Hole - Animated Fashion 5th

Looking for the one with a cat

Have to trade or sell at cost Giant Squid (2), Matryoshka, Oh Folly

\vskip 1em
Schadenfreude Foxy Stole

Looking for: Black

Have for trade or sell at cost Green, Red

\vskip 1em
haut.monde Fairy Tale necklaces

Looking for Part of your world, Tale as old as time, Care for an Apple

Have to trade or for sale at cost: Toy Alien RARE, Kill the Beast (2), Evil Thing

\vskip 1em
Tee*fy - Vintage Brownie Camera

Looking for Pink

Have for trade or sale at cost: Black, Navy, Purple, Red

\setlength{\parskip}{0.8em}












\begin{figure}
%\centering
\vskip 4em%
\begin{verbatim}
Jaden Meap!
We all hate him!
\end{verbatim}
\vskip 1em%
\caption{-- Pastebin.com/WeAllHateHim}
\vskip 3em%
\label{960px}
\end{figure}





\section{Untitled}
So it seems that the atheist rage ended up.

Come on, why all you can't live in peace? That's why crap is happening in Arab countries and Ireland, because some can't simply respect what other people believe. Atheists like HuntSaboteur really put down their choices of not believing in a God. Why you should rub in people's face? I'm a presbyterian christian (predestination FTW), most of my friends are agnostics, atheists, catholics, wiccans and jews. Two of my best friends are Satanists, and I don't rub my belief in their face that I strongly disagree on what they believe. I learned how to tolerate and be friends with anyone, no matter if they believe in a old man, a six-armed elephant or in a pedophile sci fi writer. Let people believe in what they want. You can't call religious people stupid because by being intolerant you're being a lot more stupid.

And HP Poison Unown eats Rotom-C.






\section{Untitled}
\setlength{\parskip}{0cm}
1.  Marijuana

2.  Nitrous Oxide

3.  Amphetamine

4.  Diphenhydramine

5.  Alcohol

6.  Methylenedioxymethamphetamine

7.  2C-E

8.  JWH-018

9.  Dextromethorphan

10. Hydrocodone

11. Tramadol

12. Cyclobenzaprine

13. Kava Kava

14. 1-(4-trifluoromethylphenyl)piperazine HCl

15. Hyoscyamine

16. Methadone

17. Methylone

18. Cocaine

19. Crack

20. Salvia

21. Psilocybin

22. Kratom

23. Nutmeg

24. Tobacco

25. Xanax

26. Klonopin

27. Valium

28. Promethazine

29. Baeocystis

30. Psilocin

31. Paxil

32. Pliva

33. Darvocet

34. 4-MMC

35. Ethylone

36. Etizolam

37. Methoxetamine

38. LSD

39. 5-MeO-MiPT
\setlength{\parskip}{0.8em}






\section{Nebula and \#Omegle VS Omegle Stranger}

\setlength{\parskip}{0cm}

Nebula :: hi

Nebula :: i have a problem

Stranger :: hello random stranger with a problem!

Nebula :: everytime i try to workout my nipples start secreating white liquid

Nebula :: it's really embarassing

Nebula :: what can i do?

Stranger :: try using calpol.

Nebula :: whats that?

Stranger :: http://en.wikipedia.org/wiki/Calpol [NSFW -- ADDED BY BOT]

Nebula :: i also have one breast

Nebula :: thats really embarrassing too

Stranger :: have you ever seen total recall?

Nebula :: yes

Nebula :: dont even start...

Nebula :: i already got bullied so much for that

Stranger :: a chick had three times more breast than you.

Nebula :: fuck you!

Stranger :: its a statement, a fact. no need to be offended.

Nebula :: i also have one leg which is very embarassing

Nebula :: what can i do?

Nebula :: and one eye come to think of it

Stranger :: use calpol.

Stranger :: draw another one to the left of your single eye.

Stranger :: do you know the pillow man?

Nebula :: no whats that?

Stranger :: nevermind.

Janca :: hopsin?

Stranger :: no thanks, im stuffed.

Nebula :: what did you eat?

Nebula :: that made you so stuffed

Stranger :: a big box of raisins.

Nebula :: sounds dumb

Stranger :: tasty though.

Nebula :: do you like adele

Nebula :: only people who like adele like rasins

Stranger :: she set fire to the rain. it was super-effective. so no, i dont like her.

Nebula :: well i have to go now bye person i will never meet

Stranger :: im outside.

The Stranger has disconnected.

\setlength{\parskip}{0.8em}


\vskip 1em

The length of this conversation was: 00:07:00





\section{Untitled}
\begin{verbatim}
(1) 4a + 7b = 15
(2) 8a + 2c = -48
(3) 6b + 2c = 22

(2) 8a + 2c = -48
(3)12b - 2c = -22
------------------
(4) 12b + 8a = -70
(1)-14b - 8a = -30
-------------------
-2b = -100
b = 50

6(50) + 2c = 22
 300 + 2c = 22
 
2c = -278
c = -139

8a + 2(-139) = -48
8a - 278 = -48
8a = 230
a = 28 3/4
\end{verbatim}



\section{Elves}
In contrast to the lush heartlands of Sacharia, the great steppes to the south-east are a vast region of dry grassland. With harsh weather, and little resources of wood or ore, the one thing found in abundance are the flocks of horses that live both wild and domestically. It is in this cold, arid waste that one can find the Hien Chanat, a semi-nomadic race of elven hunters and horsemen, who much like their steppe horses, are lean, hardy, swift and temperamental.

Ruled by Murat Han, the Chien are a people steeped in complicated principles of family, friendship, and personal honor. 
To make a Hien a friend is to receive a lifelong ally, to anger one is the creation of a mortal enemy.

Militarily, one can not think of the Chien without thinking of the thunder of hooves. Horses are a staple of life for the Chien, and children learn to ride almost as soon as they learn to walk. 
Famous too are they for their skill with the bow while mounted, with skilled warriors capable of delivering bow shots at a full gallop that many archers would find difficult at a standstill. 
All too common are the tales told by would-be raiders of their superior forces whittled down by galloping archers, only to be finally ripped asunder by shining blade and axe as horses flash across their hounded formation like lightning.

Although the tribes have varying degrees of freedom, they all pay tribute to the Han, who in turn must prove his worth to the nation. The seat of power is located in the city of Khalar, the largest settlement in the steppe.




\section{Never tell your password to anyone.}
\setlength{\parskip}{0cm}

SuSo.APathyFire: What?

(SZD)Colonel Jan Lesmor: u can trade me a tf2 key right?

(SZD)Colonel Jan Lesmor: if u can

(SZD)Colonel Jan Lesmor: save youre self one

(SZD)Colonel Jan Lesmor: i can get u a vip on my fav server

SuSo.APathyFire: You want me to give you a key?

(SZD)Colonel Jan Lesmor: like aint it fair?

(SZD)Colonel Jan Lesmor: 2 of  us being vip

(SZD)Colonel Jan Lesmor: u gota trade a key for vip

SuSo.APathyFire: Yeah go fuck yourself.

(SZD)Colonel Jan Lesmor: comon now

SuSo.APathyFire: First of all, you can't type.

(SZD)Colonel Jan Lesmor: im polish easy to tell?

SuSo.APathyFire: What's wrong, can't afford \$5?

(SZD)Colonel Jan Lesmor: no u can only donate iwht keys in that server

SuSo.APathyFire: Why would I give you a key?

(SZD)Colonel Jan Lesmor: u keep 1 i keep one we become vip

SuSo.APathyFire: I'm not doing that you can go fuck yourself, like I said.

(SZD)Colonel Jan Lesmor: comon just do it

SuSo.APathyFire: No. Get fucked scrub.

(SZD)Colonel Jan Lesmor: if u dont wana be a vip just igive me a key any way

SuSo.APathyFire: I fucking hate beggers.

SuSo.APathyFire: Why the fuck would I give you a key

SuSo.APathyFire: Go buy it with the money you make fucking goats.

(SZD)Colonel Jan Lesmor: thenm  u made ur self aloat of emanys on steam

SuSo.APathyFire: No

(SZD)Colonel Jan Lesmor: im the man of steam

(SZD)Colonel Jan Lesmor: suscbribed in fact

SuSo.APathyFire: I don't care.
\setlength{\parskip}{0.8em}




\section{Skrillex - First of the year}
\setlength{\parskip}{0cm}

[Eclectic Introduction]

\vskip 1em

Aeg eh euf, gyaaaa uh ah uh, gye gye gye gyeeeeuw.

Aeg eh euf, gyaaaa uh ah uh, gyuh nyi nyi nyi nyiiii nyao ni ni ni.

Aeg eh euf, gyah, ah, yef, yaaiooiiiiinaaiiooneueuaodeh.

Aeg eh euf, gyaaaa uh ah uh, gye naowenyeeehuh.

Aeg eh euf, gyaaaa uh ah uh, gyuh nyi nao seddedum.

Aeg eh euf, gyah, ah, yef, giaoaiosoiiiiinaaiiooneueuayewnudeh.

\vskip 1em

[Eclectic Breakdown]

\vskip 1em

Aeg eh euf, gyaaaa uh ah uh, gye naowenyeeehuh.

Aeg eh euf, gyaaaa uh ah uh, gyuh nyi nao seddedum.

Aeg eh euf, gyah, ah, yef, giaoaioseoiiiiinaaiio -

Call 911 now!

BWUY YOH.

GWEEEH nyen nyun nyon, GWEEEH nyen nyun nyon, NYIOAM.

BWUY YOH.

GWOH nyeh nyeh nyeh, GWOOOOP GUHWEEEE-YOOOOO.

GWEEE nyee nyee nyee nyee nyee nyee nyee nyee nyee NYIOAM.

GWEE GWOOOOHOOH nuh nuh nuh, VUSLAT,

you gah uh jah!

BWUY YOH.

GWEEEH nyen nyun nyon, GWEEEH nyen nyun nyon, NYIOAM.

BWUY YOH.

GWOH nyeh nyeh nyeh, GWOOOOP GUHWEEEE-YOOOOO.

GWEEE nyee nyee nyee nyee nyee nyee nyee nyee nyee NYIOAM.

GWEE GWOOOOHOOH nuh nuh nuh, gwish gwash gwilla bah.

\vskip 1em

BWUY YOH.

Bwohhhh widdle da widdle do woodley widdledy wawww weeeeh.

Gritchlew,

WEUUUUW, GWAAH GWOOH GRAW GRIH GRIH GRIH GREUUUUW.

GWEEE nyee nyee nyee nyee nyee nyee nyee nyee nyee REHHH sheww.

(Bwohhhh widdle da widdle do woodley widdledy wawww.)

Geh geh geh GUHWEEEE EH nuh nuh nuh,

gwish gwash,

you gah uh jah!

BWUY YOH.

Bwohhhh widdle da widdle do woodley widdledy wawww weeeeh.

Gritchlew,

WEUUUUW, GWAAH GWOOH GRAW GRIH GRIH GRIH GREUUUUW.

GWEEE nyee nyee nyee nyee nyee nyee nyee nyee nyee REHHH sheww.

(Bwohhhh widdle da widdle do woodley widdledy wawww.)

Geh geh geh GUHWEEEE EH nuh nuh nuh,

gwish gwash,

you gah uh jah!

\vskip 1em

[Eclectic Interlude]

\vskip 1em

Aeg eh euf, gyaaaa uh ah uh, gye naowenyeeehuh.

Aeg eh euf, gyaaaa uh ah uh, gyuh nyi nao seddedum.

Aeg eh euf, gyah, ah, yef, giaoaioseoiiiiinaaiio -

Call 911 now!

BWUY YOH, GWEEEH nyen nyun nyon, GWEEEH nyen nyun nyon, NYIOAM,

BWUY YOH, GWOH nyeh nyeh nyeh, GWOOOOP GUHWEEEE-YOOOOO,

GWEEE nyee nyee nyee nyee nyee nyee nyee nyee nyee NYIOAM,

GWEE GWOOOOHOOH nuh nuh nuh, gwish gwash,

niaoom unna ninny knee.

BWUY YOH.

GWEEEH nyen nyun nyon, GWEEEH nyen nyun nyon, NYIOAM.

BWUY YOH.

GWOH nyeh nyeh nyeh, GWOOOOP GUHWEEEE-YOOOOO.

GWEEE nyee nyee nyee nyee nyee nyee nyee nyee nyee NYIOAM.

GWEE GWOOOOHOOH nuh nuh nuh, gwoh shehnaaahhh.

\vskip 1em

BWUY YOH.

Bwohhhh widdle da widdle do woodley widdledy wawww weeeeh.

Gritchlew,

WEUUUUW, GWAAH GWOOH GRAW GRIH GRIH GRIH GREUUUUW.

GWEEE nyee nyee nyee nyee nyee nyee nyee nyee nyee REHHH sheww.

(Bwohhhh widdle da widdle do woodley widdledy wawww.)

Geh geh geh GUHWEEEE EH nuh nuh nuh,

gwish gwash,

you gah uh jah!

BWUY YOH.

Bwohhhh widdle da widdle do woodley widdledy wawww weeeeh.

Gritchlew,

WEUUUUW, GWAAH GWOOH GRAW GRIH GRIH GRIH GREUUUUW.

GWEEE nyee nyee nyee nyee nyee nyee nyee nyee nyee REHHH sheww.

(Bwohhhh widdle da widdle do woodley widdledy wawww)

Geh geh geh GUHWEEEE EH nuh nuh nuh,

gwish gwash,

you gah uh jah!

\vskip 1em

Aeg eh euf, gyaaaa uh ah uh, gye gye gye gyeeeeuw.

Aeg eh euf, gyaaaa uh ah uh, gyuh nyi nyi nyi nyiiii nyao ni ni ni.

Aeg eh euf, gyah, ah, yef, yaaiooiiiiinaaiiooneueuaodeh.

Aeg eh euf, gyaaaa uh ah uh, gye naowenyeeehuh.

Aeg eh euf, gyaaaa uh ah uh, gyuh nyi nao seddedum.

Aeg eh euf, gyah, ah, yef, giaoaiosoiiiiinaaiiooneueuayewnudeh.

\vskip 1em

[Eclectic Outro]
\setlength{\parskip}{0.8em}




\section{Untitled}
.o Hello, 56.187.192.13, your IP is being resolved to an address....FBI will be contacted momentarily.

.o NOTICE TO PARTICIPANT: The Federal Bureau of Investigation has logged a record of this chat along with the IP addresses of the participants due to violation of United States federal law. VIOLATION: Solicitation of a minor.

.o IMPORTANT: If you believe this chat to be logged in error, please state your reasons to the F.B.I. Monitoring agentobserving this chat and quote reference number 3744956127.

.o Failure to do so within the next 15 minutes will result in your IP address being entered in our criminal database and prosecution. 

.o Your IP address has been recorded by the Child Internet Service Protection Agency. Please wait while ref code 3744956127 is entered into the database.












\section{spaghetti story}
\setlength{\parskip}{0.0em}


\textrangle \hspace{0.1em} Walk in to BAB workshop

\textrangle \hspace{0.1em} Speak to lady to counter, saying I need a Rarity doll for my niece's birthday

\textrangle \hspace{0.1em} "Okay, but I'm afraid we're out of pre-made dolls, I'll get a skin from the back"

\textrangle \hspace{0.1em} Comes back with flat piece of fabric

\textrangle \hspace{0.1em} Inspect it, see that you need to stuff it through the ass

\textrangle \hspace{0.1em} Why

\textrangle \hspace{0.1em} No problem, just stuff it, pay, get out, no spaghetti

\textrangle \hspace{0.1em} Go to the stuffing station

\textrangle \hspace{0.1em} Begin stuffing

\textrangle \hspace{0.1em} ...thru Rarity's... glorious... marshmallow... butthole...

\textrangle \hspace{0.1em} Get boner, try best to hide it

\textrangle \hspace{0.1em} Old lady next to you, who's stuffing a Rainbow Dash for the toddler next to her, notices your erection

\textrangle \hspace{0.1em} You make momentary eye contact, can tell she's disgusted

\textrangle \hspace{0.1em} She says nothing

\textrangle \hspace{0.1em} Outside, two teenagers walk by, notice you in the store

\textrangle \hspace{0.1em} They walk in

\textrangle \hspace{0.1em} Oh shit

\textrangle \hspace{0.1em} ``Hey anon, whatcha... OH SHIT SON!''

\textrangle \hspace{0.1em} Oh god, they noticed your boner

\textrangle \hspace{0.1em} They yell to the entire store ``HEY EVERYONE, LOOK, THIS HORSEFUCKER WANTS TO HAVE SEX WITH THIS DOLL!''

\textrangle \hspace{0.1em} At that very instant, spaghetti comes shooting our of your taut pants

\textrangle \hspace{0.1em} Try to ignore everyone, just finish stuffing

\textrangle \hspace{0.1em} Spaghetti spills into the tub of stuffing

\textrangle \hspace{0.1em} Too embarrassed to notice, stuff Rarity with Spaghetti.

\textrangle \hspace{0.1em} Finished. Sew Rarity's asshole up. She's probably half full with spaghetti.

\textrangle \hspace{0.1em} Pay the cashier. Everyone in the store is laughing at you

\textrangle \hspace{0.1em} You try your best not to cry

\textrangle \hspace{0.1em} Get in your car, drive home with your doll

\textrangle \hspace{0.1em} Try hugging it, notice that there's spaghetti in her

\textrangle \hspace{0.1em} Day later, spaghetti has dried, Rarity is unhuggably crunchy


\setlength{\parskip}{0.8em}











\section{Flashback: Meta}
Lilura stared at the metamorphosis cocoon in the room she and Ockzel had cleared out.  It held the fishtroll that she'd grown up with as he rushed through sweeps' worth of growth.  They'd started spitting silk at about the same time – a small blessing, because at least then both of them were in the same boat – and it was only natural that they'd hole up in her apartment for the process.

She'd gone first, spinning her cocoon earlier than all the other limes in this cohort.  Ock had sat up and watched over it; she knew he wouldn't have left the room.  He'd hoarded enough food beforehand that he wouldn't need to.  He'd stayed in the room with her for almost two perigrees, and had food, a bath, and a comfortable recuperacoon ready for her when she clawed her her way out.  There was no one she'd want around more than him – he had run with her since they were three, taken care of her whether it was his fault or hers.  He hovered over her while she recovered, providing food without complaint when she woke at odd hours of the day and kept him away with pleas for back rubs for sore muscles.

Not two nights later, Ockzel started spitting up silk in earnest.  He tried to argue for putting it off for a few nights – she was still recovering, after all, and he could stop it if he tried – but she wasn't having any of it.  He reluctantly ate his pre-cocoon meal and then started spinning.

It wasn't obvious in the first couple of days that anything was off.  His cocoon was bright violet and quiet, carefully attached to the walls and resting safely in the corner.  The mister sprayed brine, something he'd been adamant about having before he agreed to metamorphose in her apartment.  The cooped-in boredom hadn't even begun to bother her before things began to go downhill.

The third day, the support fibers for the cocoon started to pale and fade into translucence.  The fourth night, all of the fibers did, streaking gauzy white down toward the cocoon they anchored.  Lilura's pusher flipped anxiously in her chest when she saw that, but she tried to reassure herself.  It wasn't necessarily too soon – perhaps the fact that he was a seadweller just meant that the color was changing to keep a concentration in the cocoon.

She didn't believe herself, either.  A knot of worry settled in her chest.

By the fifth day, the support fibers were completely drained of color.  The cocoon was still quiet; that was a good sign.  (Rlght?)  She had almost started to relax when, on the seventh morning, white patches began to spread on the cocoon itself.  All of the illusions she tried to tell herself crashed into so many pieces when she woke up and saw those deadly-white splotches.  There was no way that could be mistaken.

His metamorphosis was going far too quickly.  At this rate he was going to be out in a matter of days instead of weeks.  By the time the sun rose at the end of the seventh day, more than half of his cocoon was covered in white streaks.  The ninth day, his cocoon was bleached bone-white.

The worst part was the silence.  There wasn't the movement that there should have been when a normal meta gets to this point.  He should have been moving around enough that she could hear him scraping around before he woke up.  Instead, there was just dead silence.  It make her pusher skip when she let herself think about it.  She tried not to.

The knot in her chest tugged tighter.  (Maybe that was a bad way to phrase that.  Yeah, lt reaIIy was.)

By the tenth night, she had given up on trying to sleep.  Instead, she sat close to the white cocoon and stared at it.  It didn't so much as quiver.  There wasn't a single quiet “scritch” of claws on silk.  The knot in her chest had dragged so much into it that she wasn't sure that she could breathe quite right anymore.  She closed her eyes and leaned her forehead on her knees.  Pricks of pain burst in her palms when she dug her claws in; she couldn't scream, she shouldn't, it could disturb him while he slept.  She couldn't make it worse.  (As lf lt wasn't aIready beyond savlng.)

Her ears perked of their own volition when the barest whisper of a “scr” came from the cocoon.  She jolted to her feet when clear fluid began oozing from it.  She couldn't see the tear, but it had to be there.  She couldn't decide if she was more delighted that this was a sign of life or terrified of what she might see when he emerged from the cocoon.  Her breath stilled in her chest as she waited for him to emerge.

And waited.

And waited.

“Ock?  Finnikins?” she called.  When there was no answer for a long moment, her pusher seized up and froze in her chest.  Icy dread, cold as the deeps, ran down her spine.  “Ockzel?”  Silence, again.  “Ockzel, answer me, please.”  She couldn't see the tear in his cocoon.  She couldn't hear him moving.  A few moments passed with no change.

If anyone learned that she did this, she was sure she'd never be seen as respectable again.  She dug her claws into the top layer of silk and pulled.  The brittle silk tore away, peeling back in tattered ribbons to reveal a still, pale troll curled up on the still-damp bottom.  Tearing away the rest of the silk was a frantic blur; the next thing she was aware of was carefully easing him out of the ruined remains.

He was so pale.  So very, very pale.  Her fingers pressed gently against his neck and she prayed that she'd feel something, anything- and there, there, there it was, a faint and slow pulse.  And then she was hugging him, holding him, trying not to cry.

“Mm.  're w'rm.”  His voice was light, breathy, not the rich adult quality that it should have been.

“Come on, up you go,” she told him, easing him up.  Oh, he hadn't grown hardly at all.  She could feel how weak his bones were, how his muscles were limp.  Her mind raced:  she had to get him in the tank, had to get him where he could rest.  Somehow – strength born of terror had never made so much sense to her as it did now – she manhandled him into the living room, up the stairs, and into the tank.  He sank down slowly until Cuttlemom caught him, her arms writhing frantically around him.

It was good for now; he'd grown up in the same waters as Cuttlemom had.  She could- she could figure out what else to do to help it later.  She sank down with her back to the cold glass, curled her knees up to her chest, and sobbed.  They weren't out of the woods- he wasn't.  He wasn't out of the woods, not yet.  All she could do was hope that he'd be fine after a week and a half meta.

All she could do was hope.





\section{Untitled}
\begin{verbatim}
What a beautiful test I'm writing here
---------------------------------------

This is just _great_!
\end{verbatim}



\section{Untitled}
\begin{verbatim}
<?php
$this = 'sure is somethin';
\end{verbatim}






\section{Clark Kent - Super human strength}
Superhuman Strength – Clark Kent has strength that… many find to be unbelievable and a lie. His strength casts a massive shadow over all others ion earth and possibly the spiritual realm. His maximum is not even know as it seems limitless by the feats he has accomplished. Its unreal, its unusual even by today’s standards and is not used for evil. His strength is amazing, his feats known to man consist of doing the work of laborers building homes and finished in half the time a group of ten could on the project while he does it alone and only with his strength, he’s personally crushed diamonds that he had found stolen by thieves of which the original owners had long since past away before. His own weight means nothing to him, weighing in at around two hundred to three hundred pounds of pure muscle and lifting items several tons in weight over his head and throwing them like it was nothing and if that’s not enough, his fingers can break entire steel beams in half. 

Still want more info? If that wasn’t enough, lifting mountains is child's play for Clark. Its strange isn’t it?  His own wrist can do this alone, taking little to no effort to set the mountain back with no damage to it. He moved a planet even, though still not using his max to do so. He;s even shattered a meteorite the size of Texas heading towards earth with such a powerful punch that all of the small fragments burnt when he used his Heat Vision(TBE).

Back in 2012, the worlds Ice caps were melting faster than ever due to green house gases and other things influencing the worlds temperature. Clark saw reason to try and move the planet due to absorbing Yellow Solar Energy(TBE) which had increased his potential and abilities immensely. He moved it back several miles and caused the moon to loose orbit. But in this he saved the ice caps. He quickly ha forced the moon back into its proper orbit with his strength before flying off.  His maximum potential is completely unknown, but few believe he is rivaled in terms of strength. But do not think he cannot control his strength. His control is the only thing keeping him from destroying the planet when he punches the ground or something like it. The massive crater that now exists on the moon was from him using to much strength when he pushed it into orbit, almost destroying the moon completely had he not stopped when he did. 

It is believed that his strength mainly may come from his own planet and its gravity, of which was hundreds if not thousands and possibly millions of time stronger than earths own natural gravity. At the end of the 2010’s Era, Clark tested his strength and found he was able to move even Jupiter while leaving a crater once more. Now it can be seen at another red spot on Jupiter. In the sunlight, all his powers are stronger. Why? Most, if not all of his powers are fueled by solar energy. While he can fight and battle at night with ease, his power level drops enough to be matched. If the sun was ever to truly stop existing, every other star in the galaxy would fuel him instead. This is why he may fight at night, because of the stars supplying energy to him. Though don’t be fooled. He can hold his own for hundreds of years without solar energy.




\section{Untitled}
Hello!

I want to thank you for taking the time out of your busy day for me, it made me feel special, and
I stopped here to thank the Higher Power for sending you to me, and me to you. A lot of people believe
it or not does not know what a different a card, letter, phone call, e-mail, can make . To me it says to
the person recieving the card, letter, phone call that your important to take the time for.    This is
another thing I always admirer about you, is that you make time for others, and you had a million and one
things to do, but you found time to sit down and write or sent a card to me. THANK YOU!.
    You are a designer original, and one of a kind. Your fingerprints are different from anyone else-living
or dead. The same goes for your footprints, voice print, hand print, and your entire gen-tic make up.
And even if there was, which there is not, no one has been place by God in your family, neighborhood,
church, group of friends, and associates. Nobody else has has the same experience you've had. Nobody
else has the same talents, and abilities, and skills and training. Even before I was een born,God knew
I neeeded someone and he sent me the best, you!    Nobody has ever been like you. And nobody ever
will be just like you. Your are a designer original ( Psalm 139:14)
   When I was three I waited over three  hours for me dad to come out of surgery. And
that not counting the hours we waited with him before the surgery. I guess I got kind of  tired of the
snacks my mother brought for me, and the toys. I got loud, and a lady told my mother if you cannot not
kept him quiet you must leave. My mother brought out finger paint and I was happy. I made a
wonderful picture and Mom put it on the empty seat beside her to dry. Then mother otook me to the
restroom to wash up. As we got back, the doctor called our last name, and told us how my father was
doing. No one else was there for him, but us and we were so  proud to be there for him as he had been
for us.I remembering  hoping I would never have too have any thing replaced!
   That when it happen. A women leaving the waiting room had sat on my fingerprinting, and it was
stuck to her white business suit. I always wondered if she enjoyed my one of a kind creation? No other
women had my designs on hr dress. That painting fitted her like a soft leather glove fits a hand.
   This is the same women who had complaint about me and had made it clear she was glad I couldn't
be replicated. When I thank her he got really upset.
   A few weeks ago I found out my that my Doctor since birth  Dr. Moore, was force into retirement a
while back, and guess who took his place. The same lady who sat on my painting. She looked about the
same to me, and I thought she won't remember me. Wrong!
   As I walked into her office she says, " I know you!" "Your that Designer Original.
    To my mother she says, " Why didn't you tell me about the painting I was wearing?"
    My mother just smiled and told her she liked living.
    The doctor had gone to met a client, and that when she found out about my painting, and that when
she told me, she had  learned an important lesson ,and that was to laugh at herself. Her patient  never
laugh, but she did that day, they both did. My painting, was how Good took a mess an turned it into a
miracle.   However, that doctor to htis day  is still happy there is just one of me. Now, for something
I wanted to share with you, that I feel is very important.
   You walked into your doctor office. You name is  called, and you go into a private room. The nurse
writes on your chart, she leaves. Then in comes the doctor.
    It all screams of privacy right? Wrong!
Obama maded it bad.
   A women who happens to be a lawyer, found out things are not always what they appear to be, as
all her health information was available to anyone who worked at the hospital. It all kept on a
computer.
  Another women goes the a PH.D, and told what said in this room stays in this room. She thought she
was protected under the HIPAA, and doctor notes would be private

\vskip 1em
SKIPPED A PAGE
\vskip 1em


Don't trusting the psychiatrists, they always tell you you are crazy but you are Designer Original!
They just want to sell you medicine and they are bad.









\section{short story challenge}
pat loved to eat apples. one day there were no apples, so pat had to find a 
new food. at first pat didn't want to try any new foods, but one day he saw a 
bird eating ice cream. pat found birds very appealing, so he took a lick of 
the bird's ice cream and found it delectable. after taking the bird as his 
bride, pat went on to try many new foods, meeting many new brides along the 
way, but also many who tried to give pat naughty foods like mr. lawson at 
sunday school. one day pat was really tired hungry from all his jesus chores 
and bible studies when mr. lawson found us in the prayer room and told us god 
was mad at our sins but there were a few special jesus chores that we could do 
to save our parents from hell. we didnt want to do them but god said it was 
okay if we closed our eyes so now pat's parents will go to heaven and won't 
burn in hell dforever. when pat went home he killed himself but came back 
everytime. return with the elixir.








}
\end{multicols}




\end{document}
